Automated Verification and Synthesis of Cyber-Physical Systems: Advances and Challenges

### 2018-03-12 paper.tex
fixed references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Novel verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction and in a completely automatic way ({\it i.e.}, users do not need to provide loop invariants), were recently proposed~\cite{Gadelha15,Beyer15,Brain15,Rocha15,Kinductor,Rocha17}. Additionally, \textit{k}-induction based verification was also applied to ensure that (restricted) C programs (1) do not contain violations related to data races~\cite{Donaldson10}, considering the Cell BE processor, and (2) do respect time constraints, which are specified during system design phases~\cite{EenS03}. Apart from that, \textit{k}-induction is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,Sheera00,GrosseLD09}.

It is worth noticing that \textit{k}-induction with invariants has the potential to be directly integrated into existing BMC approaches, given that the induction algorithm itself can be seen as an extension after \textit{k} unwindings and it is possible to generate program invariants with other software modules, which are then translated and instrumented into an input program \cite{Rocha15}.

@@

\textbf{(RP3)} Novel approaches to model check embedded software using \textit{k}-induction and invariants were proposed and evaluated in literature, which demonstrate its effectiveness in some real-life embedded-system applications~\cite{Gadelha15,Brain15,Rocha15,Donaldson10,Rocha17}; however, the main challenge remains still open, {\it i.e.}, to compute and strengthen loop invariants for proving program correctness and timeliness in a more efficient and effective way, in order to be competitive with other model-checking approaches. In particular, invariant-generation algorithms have substantially evolved over the last years, with the goal of discovering inductive invariants of programs~\cite{pips:2013,Henry:2012} or continuously refine them during verification~\cite{Beyer15}; however, there is still a lack of studies for exploiting the combination of different invariant-generation algorithms ({\it e.g.}, interval analysis, linear inequalities, polynomial equalities and inequalities) and how to strengthen them during verification, in order to ensure system robustness w.r.t. implementation aspects. Finally, optimal configurations for invariant generators are still of paramount importance, given that applications with code based on different aspects may benefit from different setups.

@@

%\begin{thebibliography}{1}

%1
%\bibitem{Kopetz11}
%H.~Kopetz:
%\newblock {\em {Real-Time Systems - Design Principles for Distributed Embedded Applications}}.
%\newblock Real-Time Systems Series, Springer, ISBN 978-1-4419-8236-0, pp. 1--376, 2011.
%
%%2
%\bibitem{xu15}
%Xua X., Jiaa H., Wanga D., Yub D., Chiangc H.:
%\newblock {\em {Hierarchical energy management system for multi-source multi-product microgrids}}.
%\newblock In: Renewable Energy, v. 78, pp. 621--630, 2015.
%
%%3
%\bibitem{leeCPS}
%Lee E.:
%\newblock {\em {Cyber-physical Systems: Design Challenges}}.
%\newblock In: International Symposium on Object Oriented Real-Time Distributed Computing, pp. 363--369, 2008.
%
%%4
%\bibitem{leeCPS2}
%Lee E.:
%\newblock {\em {The Past, Present and Future of Cyber-Physical Systems: A Focus on Models}}. 
%\newblock In: Sensors 15(3): pp. 4837--4869, 2015.
%
%%5
%\bibitem{groza2015formal}
%Groza A., Letia I., Goron A., Zaporojan S.: 
%\newblock {\em {A formal approach for identifying assurance deficits in unmanned aerial vehicle software}}.
%\newblock In: Progress in Systems Engineering, Springer, pp. 233--239, 2015.
%
%%6
%\bibitem{Cordeiro09}
%Cordeiro L., Fischer B., Chen H., Marques-Silva J.:
%\newblock {\em {Semiformal Verification of Embedded Software in Medical Devices Considering Stringent Hardware Constraints}}.
%\newblock In: International Conference on Embedded Software and Systems, pp. 396--403, 2009.
%
%%7
%\bibitem{munir}
%Munir S., Stankovic J. A., Liang C.-J. M., Lin S.:
%\newblock {\em {Cyber Physical System Challenges for Human-in-the-Loop Control}}. 
%\newblock In: 8th International Workshop on Feedback Computing, pp. 1--4, 2013.
%
%%8
%\bibitem{Abate17}
%Abate A., Bessa I., Cattaruzza D., Cordeiro L., David C., Kesseli P., Kroening D.:
%\newblock {\em {Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants}}.
%\newblock In: 20th ACM International Conference on Hybrid Systems: Computation and Control, 2017 (to appear).
%
%%9
%\bibitem{ldd}
%Witkowski T., Blanc N., Kroening D., Weissenbacher G.:
%\newblock {\em {Model checking concurrent linux device drivers}}.
%\newblock In: 22nd IEEE/ACM international conference on Automated software engineering, pp. 501--504, 2007.
%
%%10
%\bibitem{mlembe}
%S.~Virtanen:
%\newblock {\em {Advancing Embedded Systems and Real-Time Communications with Emerging Technologies}}.
%\newblock IGI Global, ISBN 978-1466660342, pp. 1--502, 2014.
%
%%11
%\bibitem{Kroening15}
%Kroening D., Liang L., Melham T., Schrammel P., Tautschnig M.:
%\newblock {\em {Effective Verification of Low-Level Software with Nested Interrupts}}. 
%\newblock In: Design, Automation and Test in Europe, pp. 229--234, 2015.
%
%%12
%\bibitem{cudalucas}
%Monteiro F. R., da Silva Alves E. H., Silva I. S., Ismail H., Cordeiro L. C., de Lima Filho E. B.:
%\newblock {\em {ESBMC-GPU A Context-Bounded Model Checking Tool to Verify CUDA Programs}}. 
%\newblock In: Science of Computer Programming xx(y): pp. xxxx--xxxx, 2017.
%
%%13
%\bibitem{stochmodel}
%Bargmann H.:
%\newblock {\em {The role of stochastic modelling in engineering science}}.
%\newblock In: Acta Mecanica 125(1), pp. 63--71, 1997.
%
%%14
%\bibitem{Shoukry}
%Shoukry Y., Nuzzo P., Puggelli A., Sangiovanni-Vincentelli A. L., Seshia S. A., Tabuada P.:
%\newblock {\em {Secure State Estimation for Cyber Physical Systems Under Sensor Attacks: A Satisfiability Modulo Theory Approach}}.
%\newblock {IEEE} Trans. Automatic Control PP(99), pp. 1--16, 2017.
%
%%15
%\bibitem{cpsattack}
%Liu Y., Ning P., Reiter M. K.:
%\newblock {\em {“False data injection attacks against state estimation in electric power grid}}.
%\newblock In: ACM Conference on Computer and Communications Security, pp. 21--32, 2009.
%
%%16
%\bibitem{Araujo16}
%Araujo, R., Bessa, I., Cordeiro, L., Chaves Filho, J.:
%\newblock {\em{ SMT-based Verification Applied to Non-convex Optimization Problems}}. 
%\newblock In: VI Brazilian Symposium on Computing Systems Engineering, 2016 (to appear).
%
%%17
%\bibitem{Biere99}
%Biere A., Cimatti A., Clarke E., Zhu Y.:
%\newblock {\em {Symbolic Model Checking without BDDs}}. 
%\newblock In: Tools and Algorithms for Construction and Analysis of Systems, LNCS 1579, pp. 193--207, 1999.
%
%%18
%\bibitem{handbook09}
%Biere A., Heule M., van Maaren H., Walsh T., eds.:
%\newblock {\em {Handbook of Satisfiability}}.
%\newblock Volume 185 of Frontiers in Artificial Intelligence and Applications., {IOS} Press, 2009.
%
%%19
%\bibitem{BarrettSST09}
%Barrett C., Sebastiani R., Seshia S.A., Tinelli C.:
%\newblock {\em {Satisfiability Modulo Theories}}. 
%\newblock In: Volume 185 of Frontiers in Artificial Intelligence and Applications. IOS Press, pp. 825--885, 2009.
%
%%20
%\bibitem{Armando2009}
%Armando A., Mantovani J., Platania L.:
%\newblock {\em {Bounded Model Checking of Software Using SMT Solvers Instead of SAT Solvers}}. 
%\newblock In: {SPIN} Workshop on Model Checking Software, LNCS 3925, pp. 146-162, 2006.
%
%%21
%\bibitem{Bradley07}
%Bradley A., Manna Z.:
%\newblock {\em {The calculus of computation - decision procedures with applications to verification}}. 
%\newblock In: Springer, pp. I-XV, pp. 1--366, 2007.
%
%%22
%\bibitem{Thomas01}
%Thomas Ball and Sriram~K. Rajamani.
%\newblock {\em SLIC: A Specification Language for Interface Checking (of C)}.
%\newblock Technical Report MSR-TR-2001-21, Microsoft Research, 2001.
%
%%23
%\bibitem{Strichman08}
%Daniel Kroening and Ofer Strichman.
%\newblock {\em Decision Procedures: An Algorithmic Point of View}.
%\newblock Springer Publishing Company, Incorporated, 2008.
%
%%24
%\bibitem{Appel97}
%Andrew~W. Appel.
%\newblock {\em Modern Compiler Implementation in C: Basic Techniques}.
%\newblock Cambridge University Press, New York, NY, USA, 1997.
%
%%25
%\bibitem{Tseitin83}
%G.~S. Tseitin.
%\newblock On the complexity of derivation in propositional calculus.
%\newblock In {\em In J. Siekmann and G. Wrightson, editors, Automation of
%  Reasoning 2: Classical Papers on Computational Logic 1967-1970}.
% 
% %26
% \bibitem{PatarinG97}
%Jacques Patarin and Louis Goubin.
%\newblock Trapdoor one-way permutations and multivariate polynominals.
%\newblock In {\em ICICS}, {\em LNCS} 1334, pages 356--368. Springer, 1997. 
%
%%27
%\bibitem{Clarke04}
%Clarke E., Kroening D., Lerda F.:
%\newblock {\em {A Tool for Checking {ANSI-C} Programs}}.
%\newblock In: Tools and Algorithms for the Construction and Analysis of Systems. LNCS 2988, Springer Berlin Heidelberg, pp. 168--176, 2004.
%
%%28
%\bibitem{MerzFS12}
%Merz F., Falke S., Sinz C.:
%\newblock {\em {{LLBMC}: Bounded Model Checking of {C} and {C++} Programs using a Compiler {IR}}}.
%\newblock In: International Conference on Verified Software: Theories, Tools, Experiments. LNCS 7152, pp. 146--161, 2012.
%
%%29
%\bibitem{CordeiroF11}
%Cordeiro L., Fischer B.:
%\newblock {\em {Verifying Multi-threaded Software using {SMT}-based Context-Bounded Model Checking}}.
%\newblock In: International Conference on Software Engineering. pp. 331--340, 2011.
%
%%30
%\bibitem{Ivancic05}
%Ivanicic F., Shlyakhter I., Gupta A., Ganai, M.K.:
%\newblock {\em {Model Checking {C} Programs using {F-Soft}}}.
%\newblock In: International Conference on Computer Design: VLSI in Computers and Processors, pp. 297--308, 2005.
%
%%31
%\bibitem{Cordeiro12}
%Cordeiro L., Fischer B., Marques{-}Silva J.:
%\newblock {\em {{SMT}-based Bounded Model Checking for Embedded {ANSI-C} Software}}.
%\newblock {IEEE} Trans. Software Eng. 38(4), pp. 957--974, 2012.
%
%%32
%\bibitem{EenS03}
%E{\'{e}}n, N., S{\"{o}}rensson, N.:
%\newblock {\em {Temporal Induction by Incremental {SAT} Solving}}.
%\newblock Electronic Notes in Theoretical Computer Science 89(4), pp. 543 -- 560, 2003.
%
%%33
%\bibitem{Sheera00}
%Sheeran M., Singh S., St{\aa}lmarck G.:
%\newblock {\em {Checking Safety Properties using Induction and a {SAT}-solver}}.
%\newblock In: International Conference on Formal Methods in Computer-Aided Design. Springer-Verlag, pp. 108--125, 2000.
%
%%34
%\bibitem{4610935}
%{IEEE} standard for floating-point arithmetic.
%\newblock {\em IEEE Std 754-2008}, pages 1--70, Aug 2008.
%
%%35
%\bibitem{Goldberg91whatevery}
%David Goldberg.
%\newblock What every computer scientist should know about floating point
%  arithmetic.
%\newblock {\em ACM Computing Surveys}, 23(1):5--48, 1991.
%
%%36
%\bibitem{pips:2013}
%ParisTech M.:
%\newblock {\em {PIPS: Automatic Parallelizer and Code Transformation Framework}}. 
%\newblock Accessed 21 February 2016
%
%%37
%\bibitem{Henry:2012}
%Henry J., Monniaux D., Moy M.: 
%\newblock {\em {PAGAI: A Path Sensitive Static Analyser}}. 
%\newblock In: Electronic Notes in Theoretical Computer Science, pp. 15--25, 2012.
%
%%38
%\bibitem{Beyer15}
%Beyer D., Dangl M., Wendler P.:
%\newblock {\em {Boosting \textit{k}-Induction with Continuously-Refined Invariants}}.
%\newblock In: International Conference on Computer-Aided Verification, LNCS 9206, pp. 622--640, 2015.
%
%%39
%\bibitem{Gadelha15}
%Gadelha M., Ismail H., Cordeiro L.:
%\newblock {\em {Handling Loops in Bounded Model Checking of C Programs via \textit{k}-Induction}}.
%\newblock In: International Journal on Software Tools for Technology Transfer (to appear), 2015.
%\newblock http://dx.doi.org/10.1007/s10009-015-0407-9
%
%%40
%\bibitem{Brain15}
%Brain M., Joshi S., Kroening D., Schrammel P.:
%\newblock {\em {Safety Verification and Refutation by k-Invariants and \textit{k}-Induction}}.
%\newblock In: International Symposium on Static Analysis, LNCS 9291, pp. 145--161, 2015.
%
%%41
%\bibitem{Rocha15}
%Rocha H., Ismail H., Cordeiro L., Barreto R.:
%\newblock {\em {Model Checking Embedded C Software using \textit{k}-Induction and Invariants}}.
%\newblock In: V Brazilian Symposium on Computing Systems Engineering, pp. 90--95, 2015.
%
%%42
%\bibitem{Kinductor}
%Donaldson A., Haller L., Kroening D., R{\"{u}}mmer, P.:
%\newblock {\em {Software Verification using \textit{k}-Induction}}.
%\newblock In: International Symposium on Static Analysis. LNCS 6887, pp. 351--368, 2011.
%
%%43
%\bibitem{Rocha17}
%Rocha, W., Rocha, H., Ismail H., Cordeiro, L., Fischer, B.:
%\newblock {\em {DepthK: A \textit{k}-Induction Verifier Based on Invariant Inference for C Programs}}. 
%\newblock In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems, 2017 (to appear).
%
%%44
%\bibitem{Donaldson10}
%Donaldson A., Kroening D., R{\"{u}}mmer P.:
%\newblock {\em {{SCRATCH}: A Tool for Automatic Analysis of {DMA} Races}}.
%\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.
%
%%45
%\bibitem{GrosseLD09}
%Gro{\ss}e D., Le H., Drechsler R.:
%\newblock {\em {Induction-based Formal Verification of {SystemC TLM} Designs}}.
%\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.
%
%%46
%\bibitem{David15}
%C.~David, D.~Kroening, and M.~Lewis.
%\newblock {\em {Using program synthesis for program analysis}}.
%\newblock In: Logic for Programming, Artificial Intelligence, and Reasoning, LNCS 9450, pp. 483--498, 2015.
%
%%47
%\bibitem{Alur13}
%Alur R., Bod\'{\i}k R., Juniwal G., Martin M., Raghothaman M., Seshia S., Singh R., Solar-Lezama A., Torlak E., Udupa A.:
%\newblock {\em {Syntax-guided synthesis}}. 
%\newblock In: Formal Methods in Computer-Aided Design, pp. 1--8, 2013.
%
%%48
%\bibitem{sketch}
%A.~Solar-Lezama.
%\newblock {\em {Program sketching}}.
%\newblock In: International Journal on Software Tools for Technology Transfer, 15(5-6):475--495, 2013.
%
%%49
%\bibitem{Sharma14}
%R.~Sharma and A.~Aiken.
%\newblock {\em {From invariant checking to invariant inference using randomized search}}.
%\newblock In: Computer Aided Verification, LNCS 8559, pp. 88--105, 2014.
%
%%50
%\bibitem{dsv_spin2015}
%Ismail H., Bessa I., Cordeiro L., Lima Filho E., Chaves Filho J.:
%\newblock {\em {DSVerifier: A Bounded Model Checking Tool for Digital Systems}}. 
%\newblock In: International SPIN Symposium on Model Checking of Software, LNCS 9232, pp. 126--131, 2015.
%
%%51
%\bibitem{Monteiro16}
%F.~Monteiro:
%\newblock {\em {Bounded model checking of state-space digital systems: the impact of finite word-length effects on the implementation of fixed-point digital controllers based on state-space modeling}}. 
%\newblock In: 24th {ACM} {SIGSOFT} International Symposium on Foundations of Software Engineering, pp. 1151--1153, 2016.
%
%%52
%\bibitem{Bessa17}
%Bessa, I., Ismail, H., Palhares, R., Cordeiro, L., Chaves Filho, J.:
%\newblock {\em {Formal Non-Fragile Stability Verification of Digital Control Systems with Uncertainty}}. 
%\newblock In: IEEE Transactions on Computers, 2017 (to appear).
%
%%53
%\bibitem{selfcar}
%Fairley P.:
%\newblock {\em {Self-Driving Cars Have a Bicycle Problem}}.
%\newblock http://spectrum.ieee.org/transportation/self-driving/selfdriving-cars-have-a-bicycle-problem.
%
%%54
%\bibitem{BMCml}
%L.~Bortolussi, D. Milios, G, Sanguinetti.:
%\newblock {\em {Smoothed model checking for uncertain Continuous-Time Markov Chains}}.
%\newblock In:. Information and Computation, 2016.
%
%%55
%\bibitem{Behrend15}
%Behrend J., Lettnin D., Gruenhage A., Ruf J., Kropf T., Rosenstiel W.:
%\newblock {\em {Scalable and Optimized Hybrid Verification of Embedded Software}}. 
%\newblock In: J. Electronic Testing 31(2): pp. 151--166, 2015.
%
%%56
%\bibitem{Lettnin09}
%Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Sch{\"o}nknecht V., Reitemeyer S.:
%\newblock {\em {Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}}. 
%\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.
%
%%57
%\bibitem{Adouane16}
%Vilca J., Adouane L., Mezouar Y.:
%\newblock {\em {Optimal Multi-Criteria Waypoint Selection for Autonomous Vehicle Navigation in Structured Environment}}. 
%\newblock In: Journal of Intelligent and Robotic Systems 82(2): pp. 301--324, 2016.
%
%%58
%\bibitem{ECBS13}
%Ramalho M., Lopes M., Sousa F., Marques H., Cordeiro L., Fischer B.:
%\newblock {\em {SMT-Based Bounded Model Checking of C++ Programs} }.
%\newblock In: International Conference on Engineering of Computer-Based Systems, pp. 147--156, 2013.
%
%%59
%\bibitem{Pereira15}
%Pereira P.  Albuquerque H., Marques H., Silva I., Carvalho C., Santos V., Ferreira R., Cordeiro L.: 
%\newblock {\em {Verifying CUDA Programs using SMT-Based Context-Bounded Model Checking}}.
%\newblock In: ACM Symposium on Applied Computing, Software Verification and Testing Track, pp. 1648-1653, 2016. 
%
%%60
%\bibitem{Sousa15}
%Sousa F., Cordeiro L., Lima Filho E.: 
%\newblock {\em { Bounded Model Checking of C++ Programs Based on the Qt Framework.}} 
%\newblock In: Global Conference on Consumer Electronics, pp. 179--180, 2015.
%
%%61
%\bibitem{Beyer14}
%D.~Beyer 
%\newblock {\em {Status report on software verification - (competition summary {SV-COMP})}}. 
%\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 8413, pp. 373--388, 2014.
% 
%%62
%\bibitem{BeyerSVCOMP15}
%D.~Beyer:
%\newblock {\em {Software Verification and Verifiable Witnesses - (Report on SV-COMP 2015).}} 
%\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 401-416, 2015.
%
%%63
%\bibitem{KahlonWG09}
%Kahlon V., Wang C., Gupta A.:
%\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order Reduction Technique}}.
%\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.
%
%%64
%\bibitem{morse15}
%J.~Morse.
%\newblock {\em {Expressive and Efficient Bounded Model Checking of Concurrent Software}}.
%\newblock {University of Southampton, PhD Thesis}, 2015.
%
%%65
%\bibitem{Inverso14}
%Inverso O., Tomasco E., Fischer B., La Torre S., Parlato G.:
%\newblock {\em {Bounded Model Checking of Multi-threaded C Programs via Lazy Sequentialization.}}
%\newblock In: International Conference on Computer-Aided Verification, LNCS 8559, pp. 585-602, 2014.
%
%%66
%\bibitem{civl15}
%Zheng M, Rogers M, Luo Z, Dwyer M, Siegel S.
%\newblock {\em{{CIVL}: Formal Verification of Parallel Programs}}.
%\newblock In: International Conference on Automated Software Engineering, pp. 830--835, 2015.
%
%%67
%\bibitem{Grumberg05}
%Grumberg O., Lerda F., Strichman O., Theobald M.:
%\newblock {\em { Proof-guided underapproximation-widening for multi-process systems.}} 
%\newblock In: Symposium on Principles of Programming Languages, pp. 122--131, 2005.
%
%%68
%\bibitem{McMillan11}
%K.~McMillan:
%\newblock {\em {Widening and Interpolation.}} 
%\newblock In: International Symposium on Static Analysis, LCNS 6887, pp. 1, 2011.
%
%%69
%\bibitem{esbmc_controller}
%Bessa I., Abreu R., Cordeiro L., Filho J.:
%\newblock {\em {SMT-Based Bounded Model Checking of Fixed-Point Digital Controllers}.}
%\newblock In: Annual Conference of the Industrial Electronics Society, pp. 295--301, 2014.
%
%%70
%\bibitem{esbmc_filter}
%Abreu R., Cordeiro L., Filho E.:
%\newblock {\em {Verifying Fixed-Point Digital Filters using SMT-Based Bounded Model Checking}.}
%\newblock In: XXXI Brazilian Symposium on Telecommunications, 2013.
%\newblock http://dx.doi.org/10.14209/sbrt.2013.57
%
%%71
%\bibitem{JMorse15}
%Morse J., Cordeiro L., Nicole D., Fischer B.:
%\newblock {\em {Model Checking LTL Properties over ANSI-C Programs with Bounded Traces.}} 
%\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.
%
%%72
%\bibitem{Bessa16}
%Bessa I., Ismail H., Cordeiro L., Chaves Filho J.:
%\newblock {\em { Verification of Fixed-Point Digital Controllers Using Direct and Delta Forms Realizations.}} 
%\newblock In: Design Automation for Embedded Systems 20(2): pp. 95--126, 2016.
%
%%73
%\bibitem{Chaves17}
%Chaves L., Bessa I., Cordeiro L.:
%\newblock {\em { DSValidator: An Automated Counterexample Reproducibility Tool for Digital Systems}}. 
%\newblock In: CoRR abs/1610.07066, 2016.
%
%%74
%\bibitem{sbrtdaniel}
%de Mello D. P. M., de Freitas M. L., Cordeiro L., da Silva J\'unior W. S., de Bessa I. V., de Lima Filho E. B, Clavier L.:
%\newblock {\em{Verification of Magnitude and Phase Responses in Fixed-Point Digital Filters}}. 
%\newblock To appear in: Brazilian Symposium on Telecommunications and Signal Processing, pp. 1-5, 2017.
%
%%75
%\bibitem{Alves15}
%Alves E. , Cordeiro L., Lima Filho E.:
%\newblock {\em{ Fault Localization in Multi-Threaded C Programs using Bounded Model Checking}}. 
%\newblock In: Brazilian Symposium on Computing Systems Engineering, pp. 96-101, 2015.
%
%%76
%\bibitem{Garcia16}
%Garcia M. , Sousa F., Cordeiro, L., Lima Filho E.: 
%\newblock {\em{ ESBMC$^{QtOM}$: A Bounded Model Checking Tool to Verify Qt Applications}}. 
%\newblock In: International SPIN symposium on Model Checking of Software (to appear), 2016.
%
%%77
%\bibitem{Lopes:2014:GSL:2692607}
%Bruno~Cardoso Lopes and Rafael Auler.
%\newblock {\em Getting Started with LLVM Core Libraries}.
%\newblock Packt Publishing, 2014.
%
%%78
% \bibitem{clang-usage}
%Cade Metz.
%\newblock Why {A}pple?s swift language will instantly remake computer
%  programming, 204.
%\newblock http://www.wired.com/2014/07/apple-swift/.
%
%%79
%\bibitem{Jackson16}
%Jackson D., Vaziri M.:
%\newblock {\em{ Correct or usable? the limits of traditional verification (impact paper award)}}. 
%\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 11, 2016.
%
%%80
%\bibitem{MorseCNF13}
%Morse J., Cordeiro L., Nicole D., Fischer B.:
%\newblock {\em {Handling unbounded loops with {ESBMC} 1.20}}.
%\newblock In: Tools and Algorithms for the Construction and Analysis of
%  Systems. LNCS 7795, Springer Berlin Heidelberg, pp. 619--622, 2013.
%
%%81
%\bibitem{MorseRCN014}
%Morse J., Ramalho M., Cordeiro L., Nicole D., Fischer B.:
%\newblock {\em {ESBMC} 1.22.}
%\newblock In: Tools and Algorithms for the Construction and Analysis of
%  Systems. LNCS 8413, Springer Berlin Heidelberg, pp. 405--407, 2014.
%
%%82
%\bibitem{Haran15}
%Haran A., Carter M., Emmi M., Lal A., Qadeer S., Rakamaric Z.:
%\newblock {\em{ SMACK+Corral: A Modular Verifier - (Competition Contribution)}}. 
%\newblock In: 21st International Conference Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 451--454, 2015.
%
%%83
%\bibitem{Beyer16}
%Beyer, D.:
%\newblock {\em{ Reliable and Reproducible Competition Results with BenchExec and Witnesses (Report on SV-COMP 2016)}}. 
%\newblock In: 22nd International Conference Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9636, pp. 887--904, 2016.
%
%%84
%\bibitem{BeyerW15}
%Beyer D., Dangl M., Dietsch D., Heizmann M., Stahlbauer A.:
%\newblock {\em{ Witness validation and stepwise testification across software verifiers}}. 
%\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 721--733, 2015.
%
%%85
%\bibitem{RochaIFM12}
%Rocha H., Barreto R., Cordeiro L., Dias Neto A.:
%\newblock {\em{ Understanding Programming Bugs in ANSI-C Software Using Bounded Model Checking Counter-Examples}}. 
%\newblock In: International Conference on Integrated Formal Methods, LNCS 7321, pp. 128-142, 2012.
%
%%86
%\bibitem{antennasbrt}
%de Jesus A. S., rodrigues R. N., Ferreira A. N. G., Valente V. H., de Melo W. C., de Lima Filho E. B, da Silva J\'unior W. S.:
%\newblock {\em{Automatic Antenna Alignment System for Satellite Receivers Operating in C and Ku Bands}}. 
%\newblock To appear in: Brazilian Symposium on Telecommunications and Signal Processing, pp. 1-5, 2017. (in Portuguese)
%
%%87
%\bibitem{amoedo}
%Amoedo D. A., da Silva J\'unior W. S., de Lima Filho E. A.:
%\newblock {\em{Parameter Selection for SVM in Automatic Modulation Classification of Analog and Digital Signals}}. 
%\newblock In: International Telecommunications Symposium (ITS), pp. 1-5, 2014.
%
%%88
%\bibitem{mlswverif}
%Hamel L.:
%\newblock {\em {On the Use of Machine Learning in Formal Software Verification.}} 
%\newblock {Technical Report TR03-294, Dept. of Computer Science and Statistics, University of Rhode Island}, 2003.
%
%
%%89
%\bibitem{nguyen}
%Phuc N. V.,:
%\newblock {\em {The Application of Machine Learning Methods in Software Verification and Validation.}} 
%\newblock {University of Texas at Austin, master of science dissertation}, 2010.
%
%%90
%\bibitem{bridge}
%Bridge J. P.:
%\newblock {\em {Machine learning and automated theorem proving.}} 
%\newblock {Technical Report 792, Computer Laboratory, University of Cambridge}, 2010.
%
% 
% %91
%\bibitem{babic07}
%Hutter F., Babic D., Hoos H. H., Hu A. J.              
%\newblock {\em{Boosting Verification by Automatic Tuning of Decision Procedures.}}
%\newblock {In 7th International Conference Formal Methods in Computer-Aided Design {(FMCAD)}, pp. 27--34, 2007.}

%\end{thebibliography}

>>>>

Novel verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction and in a completely automatic way ({\it i.e.}, users do not need to provide loop invariants), were recently proposed~\cite{Gadelha15,Beyer15,Brain15,Kinductor,Rocha17}. Additionally, \textit{k}-induction based verification was also applied to ensure that (restricted) C programs (1) do not contain violations related to data races~\cite{Donaldson10}, considering the Cell BE processor, and (2) do respect time constraints, which are specified during system design phases~\cite{EenS03}. Apart from that, \textit{k}-induction is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,Sheera00,GrosseLD09}.

It is worth noticing that \textit{k}-induction with invariants has the potential to be directly integrated into existing BMC approaches, given that the induction algorithm itself can be seen as an extension after \textit{k} unwindings and it is possible to generate program invariants with other software modules, which are then translated and instrumented into an input program \cite{Rocha17}.

@@

\textbf{(RP3)} Novel approaches to model check embedded software using \textit{k}-induction and invariants were proposed and evaluated in literature, which demonstrate its effectiveness in some real-life embedded-system applications~\cite{Gadelha15,Brain15,Rocha17,Donaldson10}; however, the main challenge remains still open, {\it i.e.}, to compute and strengthen loop invariants for proving program correctness and timeliness in a more efficient and effective way, in order to be competitive with other model-checking approaches. In particular, invariant-generation algorithms have substantially evolved over the last years, with the goal of discovering inductive invariants of programs~\cite{pips:2013,Henry:2012} or continuously refine them during verification~\cite{Beyer15}; however, there is still a lack of studies for exploiting the combination of different invariant-generation algorithms ({\it e.g.}, interval analysis, linear inequalities, polynomial equalities and inequalities) and how to strengthen them during verification, in order to ensure system robustness w.r.t. implementation aspects. Finally, optimal configurations for invariant generators are still of paramount importance, given that applications with code based on different aspects may benefit from different setups.

@@
